Specialisation \& the Latitude-niche-breadth Hypothesis

### 2015-10-07 talk/ABC_2015.tex
introduction completed

\begin{frame}
  \titlepage
\end{frame}

@@

    \begin{center}
      Large species-richness map

    \textbf{Alyssa R. Cirtwill, Daniel B. Stouffer, Tamara N. Romanuk}

@@

    \begin{center}
      Large species-richness map

    Productivity? Envionmental stability? Speciation rates?

@@

    \begin{center}
      Large species-richness map

    \textbf{Productivity? Envionmental stability?} Speciation rates?

@@

    \footnotesize{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
  \end{frame}

@@

    \begin{columns}
    \column{1in}
    \column{1in}
      - Greater specialisation in the tropics
    \column{1in}
    \column{1in}
      - Similar specialisation at all latitudes
    \column{1in}
    \end{columns}

@@

    \begin{columns}
    \column{1in}
    \column{1in}
      - More feeding links per species in tropics
    \column{1in}
    \column{1in}
      - Similar feeding links per species at all latitudes
    \column{1in}
    \end{columns}

>>>>

% \begin{frame}
%   \titlepage
% \end{frame}

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}

      \vspace{1cm}

    \textbf{Alyssa R. Cirtwill}, Daniel B. Stouffer, Tamara N. Romanuk

    \vspace{1cm}

    23 October 2015 | ABC 2015

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}

      \vspace{1cm}

      Envionmental stability? 
      Productivity? 
      Speciation rates?

      \vspace{1cm}
      {\color{white} 23 October 2015 | ABC 2015}
    \end{center}
  \end{frame}

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}

      \vspace{1cm}

      \textbf{Envionmental stability?} 
      \textbf{Productivity?} 
      Speciation rates?

      \vspace{1cm}
      {\color{white} 23 October 2015 | ABC 2015}

@@

    \tiny{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
  \end{frame}

@@

    \begin{columns}
    \column{.5in}
    \column{1.75in}
      - Greater specialisation in the tropics
    \column{.5in}
    \column{1.75in}
      - Similar specialisation at all latitudes
    \column{.5in}
    \end{columns}

@@

    \begin{columns}
    \column{.5in}
    \column{1.75in}
      - More feeding links per species in tropics
    \column{.5in}
    \column{1.75in}
      - Similar feeding links per species at all latitudes
    \column{.5in}
    \end{columns}

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/LittleRockLake.eps}

    195 food webs \\
    0-78 degrees (absolute latitude) \\
    Mean L/S, Generality, Vulnerability

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/LittleRockLake.eps}

    195 food webs \\
    0-78 degrees (absolute latitude) \\
    Mean \textbf{L/S}, Generality, Vulnerability
